---
title: "Comp 4b ratios of TD and TIC"
author: "Anshul Gupta"
date: "27/06/2014"
output: html_document
---

## Motive
TIC traces are the ones having both COMP 4b and COMP 4c values of an execution.  
The idea is to check the stablity of the execution when compiled with TIC instrumentation enabled w.r.t the execution when compiled with normal TD instrumentation.

## Overview
Multiple TIC (Time Independent Calibrated) and TD traces were acquired on graphene cluster for LU benchmark, class C and 16 processes.  
Their **COMP 4b** global values were parsed using _scripts/Expand.java_ code with
this format.  
See _org/analysis.org_

```{r Init}
setwd('..')
dataset.td.lu.16.I<-read.table("datasets/td.lu.C.16.comp.4b.I", header=TRUE)
dataset.td.lu.16.II<-read.table("datasets/td.lu.C.16.comp.4b.II", header=TRUE)
dataset.td.lu.16.III<-read.table("datasets/td.lu.C.16.comp.4b.III", header=TRUE)
dataset.td.lu.16.IV<-read.table("datasets/td.lu.C.16.comp.4b.IV", header=TRUE)
dataset.td.lu.16.V<-read.table("datasets/td.lu.C.16.comp.4b.V", header=TRUE)
dataset.tic.lu.16.I<-read.table("datasets/tic.lu.C.16.comp.4b.I", header=TRUE)
dataset.tic.lu.16.II<-read.table("datasets/tic.lu.C.16.comp.4b.II", header=TRUE)
dataset.tic.lu.16.III<-read.table("datasets/tic.lu.C.16.comp.4b.III", header=TRUE)
dataset.tic.lu.16.IV<-read.table("datasets/tic.lu.C.16.comp.4b.IV", header=TRUE)
dataset.tic.lu.16.V<-read.table("datasets/tic.lu.C.16.comp.4b.V", header=TRUE)
```

The variables are named as `d<A>_<B>`,  
where `<A>` is the Time Dependent dataset and `<B>` is the Time Independent Calibrated dataset.  
Each `d<A>_<B>` has 7 fields:

* xlabel = eventID_subblock
* avgTD = Average of time dependent trace A
* minTD = Minimum of time dependent trace A
* maxTD = Maximum of time dependent trace A
* avgTI = Average of time dependent calibrated trace B
* minTI = Minimum of time dependent calibrated trace B
* maxTI = Maximum of time dependent calibrated trace B

```{r Read datasets}
dI_I<-data.frame(xlabel=paste(dataset.td.lu.16.I$eventID, dataset.td.lu.16.I$subblock, sep="_"),
avgTD=dataset.td.lu.16.I$avg, minTD=dataset.td.lu.16.I$min, maxTD=dataset.td.lu.16.I$max,
avgTI=dataset.tic.lu.16.I$avg, minTI=dataset.tic.lu.16.I$min, maxTI=dataset.tic.lu.16.I$max,
ratioavg=dataset.td.lu.16.I$avg/dataset.tic.lu.16.I$avg,
ratiomin=dataset.td.lu.16.I$min/dataset.tic.lu.16.I$min,
ratiomax=dataset.td.lu.16.I$max/dataset.tic.lu.16.I$max)

dI_II<-data.frame(xlabel=paste(dataset.td.lu.16.I$eventID, dataset.td.lu.16.I$subblock, sep="_"),
avgTD=dataset.td.lu.16.I$avg, minTD=dataset.td.lu.16.I$min, maxTD=dataset.td.lu.16.I$max,
avgTI=dataset.tic.lu.16.II$avg, minTI=dataset.tic.lu.16.II$min, maxTI=dataset.tic.lu.16.II$max,
ratioavg=dataset.td.lu.16.I$avg/dataset.tic.lu.16.II$avg,
ratiomin=dataset.td.lu.16.I$min/dataset.tic.lu.16.II$min,
ratiomax=dataset.td.lu.16.I$max/dataset.tic.lu.16.II$max)

dI_III<-data.frame(xlabel=paste(dataset.td.lu.16.I$eventID, dataset.td.lu.16.I$subblock, sep="_"),
avgTD=dataset.td.lu.16.I$avg, minTD=dataset.td.lu.16.I$min, maxTD=dataset.td.lu.16.I$max,
avgTI=dataset.tic.lu.16.III$avg, minTI=dataset.tic.lu.16.III$min, maxTI=dataset.tic.lu.16.III$max,
ratioavg=dataset.td.lu.16.I$avg/dataset.tic.lu.16.III$avg,
ratiomin=dataset.td.lu.16.I$min/dataset.tic.lu.16.III$min,
ratiomax=dataset.td.lu.16.I$max/dataset.tic.lu.16.III$max)

dI_IV<-data.frame(xlabel=paste(dataset.td.lu.16.I$eventID, dataset.td.lu.16.I$subblock, sep="_"),
avgTD=dataset.td.lu.16.I$avg, minTD=dataset.td.lu.16.I$min, maxTD=dataset.td.lu.16.I$max,
avgTI=dataset.tic.lu.16.IV$avg, minTI=dataset.tic.lu.16.IV$min, maxTI=dataset.tic.lu.16.IV$max,
ratioavg=dataset.td.lu.16.I$avg/dataset.tic.lu.16.IV$avg,
ratiomin=dataset.td.lu.16.I$min/dataset.tic.lu.16.IV$min,
ratiomax=dataset.td.lu.16.I$max/dataset.tic.lu.16.IV$max)

dI_V<-data.frame(xlabel=paste(dataset.td.lu.16.I$eventID, dataset.td.lu.16.I$subblock, sep="_"),
avgTD=dataset.td.lu.16.I$avg, minTD=dataset.td.lu.16.I$min, maxTD=dataset.td.lu.16.I$max,
avgTI=dataset.tic.lu.16.V$avg, minTI=dataset.tic.lu.16.V$min, maxTI=dataset.tic.lu.16.V$max,
ratioavg=dataset.td.lu.16.I$avg/dataset.tic.lu.16.V$avg,
ratiomin=dataset.td.lu.16.I$min/dataset.tic.lu.16.V$min,
ratiomax=dataset.td.lu.16.I$max/dataset.tic.lu.16.V$max)

dII_I<-data.frame(xlabel=paste(dataset.td.lu.16.II$eventID, dataset.td.lu.16.II$subblock, sep="_"),
avgTD=dataset.td.lu.16.II$avg, minTD=dataset.td.lu.16.II$min, maxTD=dataset.td.lu.16.II$max,
avgTI=dataset.tic.lu.16.I$avg, minTI=dataset.tic.lu.16.I$min, maxTI=dataset.tic.lu.16.I$max,
ratioavg=dataset.td.lu.16.II$avg/dataset.tic.lu.16.I$avg,
ratiomin=dataset.td.lu.16.II$min/dataset.tic.lu.16.I$min,
ratiomax=dataset.td.lu.16.II$max/dataset.tic.lu.16.I$max)

dII_II<-data.frame(xlabel=paste(dataset.td.lu.16.II$eventID, dataset.td.lu.16.II$subblock, sep="_"),
avgTD=dataset.td.lu.16.II$avg, minTD=dataset.td.lu.16.II$min, maxTD=dataset.td.lu.16.II$max,
avgTI=dataset.tic.lu.16.II$avg, minTI=dataset.tic.lu.16.II$min, maxTI=dataset.tic.lu.16.II$max,
ratioavg=dataset.td.lu.16.II$avg/dataset.tic.lu.16.II$avg,
ratiomin=dataset.td.lu.16.II$min/dataset.tic.lu.16.II$min,
ratiomax=dataset.td.lu.16.II$max/dataset.tic.lu.16.II$max)

dII_III<-data.frame(xlabel=paste(dataset.td.lu.16.II$eventID, dataset.td.lu.16.II$subblock, sep="_"),
avgTD=dataset.td.lu.16.II$avg, minTD=dataset.td.lu.16.II$min, maxTD=dataset.td.lu.16.II$max,
avgTI=dataset.tic.lu.16.III$avg, minTI=dataset.tic.lu.16.III$min, maxTI=dataset.tic.lu.16.III$max,
ratioavg=dataset.td.lu.16.II$avg/dataset.tic.lu.16.III$avg,
ratiomin=dataset.td.lu.16.II$min/dataset.tic.lu.16.III$min,
ratiomax=dataset.td.lu.16.II$max/dataset.tic.lu.16.III$max)

dII_IV<-data.frame(xlabel=paste(dataset.td.lu.16.II$eventID, dataset.td.lu.16.II$subblock, sep="_"),
avgTD=dataset.td.lu.16.II$avg, minTD=dataset.td.lu.16.II$min, maxTD=dataset.td.lu.16.II$max,
avgTI=dataset.tic.lu.16.IV$avg, minTI=dataset.tic.lu.16.IV$min, maxTI=dataset.tic.lu.16.IV$max,
ratioavg=dataset.td.lu.16.II$avg/dataset.tic.lu.16.IV$avg,
ratiomin=dataset.td.lu.16.II$min/dataset.tic.lu.16.IV$min,
ratiomax=dataset.td.lu.16.II$max/dataset.tic.lu.16.IV$max)

dII_V<-data.frame(xlabel=paste(dataset.td.lu.16.II$eventID, dataset.td.lu.16.II$subblock, sep="_"),
avgTD=dataset.td.lu.16.II$avg, minTD=dataset.td.lu.16.II$min, maxTD=dataset.td.lu.16.II$max,
avgTI=dataset.tic.lu.16.V$avg, minTI=dataset.tic.lu.16.V$min, maxTI=dataset.tic.lu.16.V$max,
ratioavg=dataset.td.lu.16.II$avg/dataset.tic.lu.16.V$avg,
ratiomin=dataset.td.lu.16.II$min/dataset.tic.lu.16.V$min,
ratiomax=dataset.td.lu.16.II$max/dataset.tic.lu.16.V$max)

dIII_I<-data.frame(xlabel=paste(dataset.td.lu.16.III$eventID, dataset.td.lu.16.III$subblock, sep="_"),
avgTD=dataset.td.lu.16.III$avg, minTD=dataset.td.lu.16.III$min, maxTD=dataset.td.lu.16.III$max,
avgTI=dataset.tic.lu.16.I$avg, minTI=dataset.tic.lu.16.I$min, maxTI=dataset.tic.lu.16.I$max,
ratioavg=dataset.td.lu.16.III$avg/dataset.tic.lu.16.I$avg,
ratiomin=dataset.td.lu.16.III$min/dataset.tic.lu.16.I$min,
ratiomax=dataset.td.lu.16.III$max/dataset.tic.lu.16.I$max)

dIII_II<-data.frame(xlabel=paste(dataset.td.lu.16.III$eventID, dataset.td.lu.16.III$subblock, sep="_"),
avgTD=dataset.td.lu.16.III$avg, minTD=dataset.td.lu.16.III$min, maxTD=dataset.td.lu.16.III$max,
avgTI=dataset.tic.lu.16.II$avg, minTI=dataset.tic.lu.16.II$min, maxTI=dataset.tic.lu.16.II$max,
ratioavg=dataset.td.lu.16.III$avg/dataset.tic.lu.16.II$avg,
ratiomin=dataset.td.lu.16.III$min/dataset.tic.lu.16.II$min,
ratiomax=dataset.td.lu.16.III$max/dataset.tic.lu.16.II$max)

dIII_III<-data.frame(xlabel=paste(dataset.td.lu.16.III$eventID, dataset.td.lu.16.III$subblock, sep="_"),
avgTD=dataset.td.lu.16.III$avg, minTD=dataset.td.lu.16.III$min, maxTD=dataset.td.lu.16.III$max,
avgTI=dataset.tic.lu.16.III$avg, minTI=dataset.tic.lu.16.III$min, maxTI=dataset.tic.lu.16.III$max,
ratioavg=dataset.td.lu.16.III$avg/dataset.tic.lu.16.III$avg,
ratiomin=dataset.td.lu.16.III$min/dataset.tic.lu.16.III$min,
ratiomax=dataset.td.lu.16.III$max/dataset.tic.lu.16.III$max)

dIII_IV<-data.frame(xlabel=paste(dataset.td.lu.16.III$eventID, dataset.td.lu.16.III$subblock, sep="_"),
avgTD=dataset.td.lu.16.III$avg, minTD=dataset.td.lu.16.III$min, maxTD=dataset.td.lu.16.III$max,
avgTI=dataset.tic.lu.16.IV$avg, minTI=dataset.tic.lu.16.IV$min, maxTI=dataset.tic.lu.16.IV$max,
ratioavg=dataset.td.lu.16.III$avg/dataset.tic.lu.16.IV$avg,
ratiomin=dataset.td.lu.16.III$min/dataset.tic.lu.16.IV$min,
ratiomax=dataset.td.lu.16.III$max/dataset.tic.lu.16.IV$max)

dIII_V<-data.frame(xlabel=paste(dataset.td.lu.16.III$eventID, dataset.td.lu.16.III$subblock, sep="_"),
avgTD=dataset.td.lu.16.III$avg, minTD=dataset.td.lu.16.III$min, maxTD=dataset.td.lu.16.III$max,
avgTI=dataset.tic.lu.16.V$avg, minTI=dataset.tic.lu.16.V$min, maxTI=dataset.tic.lu.16.V$max,
ratioavg=dataset.td.lu.16.III$avg/dataset.tic.lu.16.V$avg,
ratiomin=dataset.td.lu.16.III$min/dataset.tic.lu.16.V$min,
ratiomax=dataset.td.lu.16.III$max/dataset.tic.lu.16.V$max)

dIV_I<-data.frame(xlabel=paste(dataset.td.lu.16.IV$eventID, dataset.td.lu.16.IV$subblock, sep="_"),
avgTD=dataset.td.lu.16.IV$avg, minTD=dataset.td.lu.16.IV$min, maxTD=dataset.td.lu.16.IV$max,
avgTI=dataset.tic.lu.16.I$avg, minTI=dataset.tic.lu.16.I$min, maxTI=dataset.tic.lu.16.I$max,
ratioavg=dataset.td.lu.16.IV$avg/dataset.tic.lu.16.I$avg,
ratiomin=dataset.td.lu.16.IV$min/dataset.tic.lu.16.I$min,
ratiomax=dataset.td.lu.16.IV$max/dataset.tic.lu.16.I$max)

dIV_II<-data.frame(xlabel=paste(dataset.td.lu.16.IV$eventID, dataset.td.lu.16.IV$subblock, sep="_"),
avgTD=dataset.td.lu.16.IV$avg, minTD=dataset.td.lu.16.IV$min, maxTD=dataset.td.lu.16.IV$max,
avgTI=dataset.tic.lu.16.II$avg, minTI=dataset.tic.lu.16.II$min, maxTI=dataset.tic.lu.16.II$max,
ratioavg=dataset.td.lu.16.IV$avg/dataset.tic.lu.16.II$avg,
ratiomin=dataset.td.lu.16.IV$min/dataset.tic.lu.16.II$min,
ratiomax=dataset.td.lu.16.IV$max/dataset.tic.lu.16.II$max)

dIV_III<-data.frame(xlabel=paste(dataset.td.lu.16.IV$eventID, dataset.td.lu.16.IV$subblock, sep="_"),
avgTD=dataset.td.lu.16.IV$avg, minTD=dataset.td.lu.16.IV$min, maxTD=dataset.td.lu.16.IV$max,
avgTI=dataset.tic.lu.16.III$avg, minTI=dataset.tic.lu.16.III$min, maxTI=dataset.tic.lu.16.III$max,
ratioavg=dataset.td.lu.16.IV$avg/dataset.tic.lu.16.III$avg,
ratiomin=dataset.td.lu.16.IV$min/dataset.tic.lu.16.III$min,
ratiomax=dataset.td.lu.16.IV$max/dataset.tic.lu.16.III$max)

dIV_IV<-data.frame(xlabel=paste(dataset.td.lu.16.IV$eventID, dataset.td.lu.16.IV$subblock, sep="_"),
avgTD=dataset.td.lu.16.IV$avg, minTD=dataset.td.lu.16.IV$min, maxTD=dataset.td.lu.16.IV$max,
avgTI=dataset.tic.lu.16.IV$avg, minTI=dataset.tic.lu.16.IV$min, maxTI=dataset.tic.lu.16.IV$max,
ratioavg=dataset.td.lu.16.IV$avg/dataset.tic.lu.16.IV$avg,
ratiomin=dataset.td.lu.16.IV$min/dataset.tic.lu.16.IV$min,
ratiomax=dataset.td.lu.16.IV$max/dataset.tic.lu.16.IV$max)

dIV_V<-data.frame(xlabel=paste(dataset.td.lu.16.IV$eventID, dataset.td.lu.16.IV$subblock, sep="_"),
avgTD=dataset.td.lu.16.IV$avg, minTD=dataset.td.lu.16.IV$min, maxTD=dataset.td.lu.16.IV$max,
avgTI=dataset.tic.lu.16.V$avg, minTI=dataset.tic.lu.16.V$min, maxTI=dataset.tic.lu.16.V$max,
ratioavg=dataset.td.lu.16.IV$avg/dataset.tic.lu.16.V$avg,
ratiomin=dataset.td.lu.16.IV$min/dataset.tic.lu.16.V$min,
ratiomax=dataset.td.lu.16.IV$max/dataset.tic.lu.16.V$max)

dV_I<-data.frame(xlabel=paste(dataset.td.lu.16.V$eventID, dataset.td.lu.16.V$subblock, sep="_"),
avgTD=dataset.td.lu.16.V$avg, minTD=dataset.td.lu.16.V$min, maxTD=dataset.td.lu.16.V$max,
avgTI=dataset.tic.lu.16.I$avg, minTI=dataset.tic.lu.16.I$min, maxTI=dataset.tic.lu.16.I$max,
ratioavg=dataset.td.lu.16.V$avg/dataset.tic.lu.16.I$avg,
ratiomin=dataset.td.lu.16.V$min/dataset.tic.lu.16.I$min,
ratiomax=dataset.td.lu.16.V$max/dataset.tic.lu.16.I$max)

dV_II<-data.frame(xlabel=paste(dataset.td.lu.16.V$eventID, dataset.td.lu.16.V$subblock, sep="_"),
avgTD=dataset.td.lu.16.V$avg, minTD=dataset.td.lu.16.V$min, maxTD=dataset.td.lu.16.V$max,
avgTI=dataset.tic.lu.16.II$avg, minTI=dataset.tic.lu.16.II$min, maxTI=dataset.tic.lu.16.II$max,
ratioavg=dataset.td.lu.16.V$avg/dataset.tic.lu.16.II$avg,
ratiomin=dataset.td.lu.16.V$min/dataset.tic.lu.16.II$min,
ratiomax=dataset.td.lu.16.V$max/dataset.tic.lu.16.II$max)

dV_III<-data.frame(xlabel=paste(dataset.td.lu.16.V$eventID, dataset.td.lu.16.V$subblock, sep="_"),
avgTD=dataset.td.lu.16.V$avg, minTD=dataset.td.lu.16.V$min, maxTD=dataset.td.lu.16.V$max,
avgTI=dataset.tic.lu.16.III$avg, minTI=dataset.tic.lu.16.III$min, maxTI=dataset.tic.lu.16.III$max,
ratioavg=dataset.td.lu.16.V$avg/dataset.tic.lu.16.III$avg,
ratiomin=dataset.td.lu.16.V$min/dataset.tic.lu.16.III$min,
ratiomax=dataset.td.lu.16.V$max/dataset.tic.lu.16.III$max)

dV_IV<-data.frame(xlabel=paste(dataset.td.lu.16.V$eventID, dataset.td.lu.16.V$subblock, sep="_"),
avgTD=dataset.td.lu.16.V$avg, minTD=dataset.td.lu.16.V$min, maxTD=dataset.td.lu.16.V$max,
avgTI=dataset.tic.lu.16.IV$avg, minTI=dataset.tic.lu.16.IV$min, maxTI=dataset.tic.lu.16.IV$max,
ratioavg=dataset.td.lu.16.V$avg/dataset.tic.lu.16.IV$avg,
ratiomin=dataset.td.lu.16.V$min/dataset.tic.lu.16.IV$min,
ratiomax=dataset.td.lu.16.V$max/dataset.tic.lu.16.IV$max)

dV_V<-data.frame(xlabel=paste(dataset.td.lu.16.V$eventID, dataset.td.lu.16.V$subblock, sep="_"),
avgTD=dataset.td.lu.16.V$avg, minTD=dataset.td.lu.16.V$min, maxTD=dataset.td.lu.16.V$max,
avgTI=dataset.tic.lu.16.V$avg, minTI=dataset.tic.lu.16.V$min, maxTI=dataset.tic.lu.16.V$max,
ratioavg=dataset.td.lu.16.V$avg/dataset.tic.lu.16.V$avg,
ratiomin=dataset.td.lu.16.V$min/dataset.tic.lu.16.V$min,
ratiomax=dataset.td.lu.16.V$max/dataset.tic.lu.16.V$max)
```

### The mean averages are calculated as:

```{r Calculate Mean Averages}
mean.avg<-matrix(0, 5, 5)
mean.avg[1,]<-c(mean(dI_I$ratioavg), mean(dI_II$ratioavg), mean(dI_III$ratioavg), mean(dI_IV$ratioavg), mean(dI_V$ratioavg))
mean.avg[2,]<-c(mean(dII_I$ratioavg), mean(dII_II$ratioavg), mean(dII_III$ratioavg), mean(dII_IV$ratioavg), mean(dII_V$ratioavg))
mean.avg[3,]<-c(mean(dIII_I$ratioavg), mean(dIII_II$ratioavg), mean(dIII_III$ratioavg), mean(dIII_IV$ratioavg), mean(dIII_V$ratioavg))
mean.avg[4,]<-c(mean(dIV_I$ratioavg), mean(dIV_II$ratioavg), mean(dIV_III$ratioavg), mean(dIV_IV$ratioavg), mean(dIV_V$ratioavg))
mean.avg[5,]<-c(mean(dV_I$ratioavg), mean(dV_II$ratioavg), mean(dV_III$ratioavg), mean(dV_IV$ratioavg), mean(dV_V$ratioavg))
print(mean.avg)
```

### The mean mins are calculated as: 

```{r Calculate Mean Mins}
mean.min<-matrix(0, 5, 5)
mean.min[1,]<-c(mean(dI_I$ratiomin), mean(dI_II$ratiomin), mean(dI_III$ratiomin), mean(dI_IV$ratiomin), mean(dI_V$ratiomin))
mean.min[2,]<-c(mean(dII_I$ratiomin), mean(dII_II$ratiomin), mean(dII_III$ratiomin), mean(dII_IV$ratiomin), mean(dII_V$ratiomin))
mean.min[3,]<-c(mean(dIII_I$ratiomin), mean(dIII_II$ratiomin), mean(dIII_III$ratiomin), mean(dIII_IV$ratiomin), mean(dIII_V$ratiomin))
mean.min[4,]<-c(mean(dIV_I$ratiomin), mean(dIV_II$ratiomin), mean(dIV_III$ratiomin), mean(dIV_IV$ratiomin), mean(dIV_V$ratiomin))
mean.min[5,]<-c(mean(dV_I$ratiomin), mean(dV_II$ratiomin), mean(dV_III$ratiomin), mean(dV_IV$ratiomin), mean(dV_V$ratiomin))
print(mean.min)
```


### The mean maxs are calculated as:

```{r Calculate Mean Maxs}
mean.max<-matrix(0, 5, 5)
mean.max[1,]<-c(mean(dI_I$ratiomax), mean(dI_II$ratiomax), mean(dI_III$ratiomax), mean(dI_IV$ratiomax), mean(dI_V$ratiomax))
mean.max[2,]<-c(mean(dII_I$ratiomax), mean(dII_II$ratiomax), mean(dII_III$ratiomax), mean(dII_IV$ratiomax), mean(dII_V$ratiomax))
mean.max[3,]<-c(mean(dIII_I$ratiomax), mean(dIII_II$ratiomax), mean(dIII_III$ratiomax), mean(dIII_IV$ratiomax), mean(dIII_V$ratiomax))
mean.max[4,]<-c(mean(dIV_I$ratiomax), mean(dIV_II$ratiomax), mean(dIV_III$ratiomax), mean(dIV_IV$ratiomax), mean(dIV_V$ratiomax))
mean.max[5,]<-c(mean(dV_I$ratiomax), mean(dV_II$ratiomax), mean(dV_III$ratiomax), mean(dV_IV$ratiomax), mean(dV_V$ratiomax))
print(mean.max)
```

## Conclusion
The TIC execution is a little slow compared to TD but the ratios are quite stable. This is accounted be the extra time taken by insturmentation (PAPI Counters).   
If this becomes an accuracy issue at some point, either we apply some correction factor or use two distinct traces (one for the instructions, one for timings).