---
title: "Rough Estimation of Instruction Rate with indivudial bins"
author: "Anshul Gupta"
date: "29/06/2014"
output: html_document
---

## Motive
Calculate the instruction rate of execution using TIC traces but having the data of individual bins instead of the global values.  
The idea is that global values may hide some information. For some events, we have 1 bin with smaller number/time and another with larger values.  
Sometimes it is really different (1 really small and big ones), sometime we can guess that for some iterations (or processes) there were less computations to do.

## Overview
5 traces with TIC instrumentation of LU benchmark, class C and 16
processes were acquired on graphene cluster.
Their **COMP 4b** and **COMP 4c** global average values and involved
processes were parsed using the _scripts/Expand.java_ code with this format.
See _org/analysis.org_

```{r Init}
setwd('..')
library(ggplot2)
tic.lu.C.16.comp.4b.bins.I<-read.table("datasets/tic.lu.C.16.comp.4b.bins.I", header=TRUE)
tic.lu.C.16.comp.4b.bins.II<-read.table("datasets/tic.lu.C.16.comp.4b.bins.II", header=TRUE)
tic.lu.C.16.comp.4b.bins.III<-read.table("datasets/tic.lu.C.16.comp.4b.bins.III", header=TRUE)
tic.lu.C.16.comp.4b.bins.IV<-read.table("datasets/tic.lu.C.16.comp.4b.bins.IV", header=TRUE)
tic.lu.C.16.comp.4b.bins.V<-read.table("datasets/tic.lu.C.16.comp.4b.bins.V", header=TRUE)

tic.lu.C.16.comp.4c.bins.I<-read.table("datasets/tic.lu.C.16.comp.4c.bins.I", header=TRUE)
tic.lu.C.16.comp.4c.bins.II<-read.table("datasets/tic.lu.C.16.comp.4c.bins.II", header=TRUE)
tic.lu.C.16.comp.4c.bins.III<-read.table("datasets/tic.lu.C.16.comp.4c.bins.III", header=TRUE)
tic.lu.C.16.comp.4c.bins.IV<-read.table("datasets/tic.lu.C.16.comp.4c.bins.IV", header=TRUE)
tic.lu.C.16.comp.4c.bins.V<-read.table("datasets/tic.lu.C.16.comp.4c.bins.V", header=TRUE)
```

```{r Read datasets}
d.C.16.4b.4c.bins.I<-data.frame(eventID=tic.lu.C.16.comp.4b.bins.I$eventID,
                                subblock=tic.lu.C.16.comp.4b.bins.I$subblock,
                                binID=tic.lu.C.16.comp.4b.bins.I$binID,
                                time.elements=tic.lu.C.16.comp.4b.bins.I$elements,
                                time.min=tic.lu.C.16.comp.4b.bins.I$minimum,
                                time.avg=tic.lu.C.16.comp.4b.bins.I$average,
                                time.max=tic.lu.C.16.comp.4b.bins.I$maximum,
                                inst.elements=tic.lu.C.16.comp.4c.bins.I$elements,
                                inst.min=tic.lu.C.16.comp.4c.bins.I$minimum,
                                inst.avg=tic.lu.C.16.comp.4c.bins.I$average,
                                inst.max=tic.lu.C.16.comp.4c.bins.I$maximum)

d.C.16.4b.4c.bins.I<-d.C.16.4b.4c.bins.I[!(d.C.16.4b.4c.bins.I$time.elements==0 & d.C.16.4b.4c.bins.I$inst.elements==0),]

d.C.16.4b.4c.bins.II<-data.frame(eventID=tic.lu.C.16.comp.4b.bins.II$eventID,
                                subblock=tic.lu.C.16.comp.4b.bins.II$subblock,
                                binID=tic.lu.C.16.comp.4b.bins.II$binID,
                                time.elements=tic.lu.C.16.comp.4b.bins.II$elements,
                                time.min=tic.lu.C.16.comp.4b.bins.II$minimum,
                                time.avg=tic.lu.C.16.comp.4b.bins.II$average,
                                time.max=tic.lu.C.16.comp.4b.bins.II$maximum,
                                inst.elements=tic.lu.C.16.comp.4c.bins.II$elements,
                                inst.min=tic.lu.C.16.comp.4c.bins.II$minimum,
                                inst.avg=tic.lu.C.16.comp.4c.bins.II$average,
                                inst.max=tic.lu.C.16.comp.4c.bins.II$maximum)

d.C.16.4b.4c.bins.II<-d.C.16.4b.4c.bins.II[!(d.C.16.4b.4c.bins.II$time.elements==0 & d.C.16.4b.4c.bins.II$inst.elements==0),]

d.C.16.4b.4c.bins.III<-data.frame(eventID=tic.lu.C.16.comp.4b.bins.III$eventID,
                                subblock=tic.lu.C.16.comp.4b.bins.III$subblock,
                                binID=tic.lu.C.16.comp.4b.bins.III$binID,
                                time.elements=tic.lu.C.16.comp.4b.bins.III$elements,
                                time.min=tic.lu.C.16.comp.4b.bins.III$minimum,
                                time.avg=tic.lu.C.16.comp.4b.bins.III$average,
                                time.max=tic.lu.C.16.comp.4b.bins.III$maximum,
                                inst.elements=tic.lu.C.16.comp.4c.bins.III$elements,
                                inst.min=tic.lu.C.16.comp.4c.bins.III$minimum,
                                inst.avg=tic.lu.C.16.comp.4c.bins.III$average,
                                inst.max=tic.lu.C.16.comp.4c.bins.III$maximum)

d.C.16.4b.4c.bins.III<-d.C.16.4b.4c.bins.III[!(d.C.16.4b.4c.bins.III$time.elements==0 & d.C.16.4b.4c.bins.III$inst.elements==0),]

d.C.16.4b.4c.bins.IV<-data.frame(eventID=tic.lu.C.16.comp.4b.bins.IV$eventID,
                                subblock=tic.lu.C.16.comp.4b.bins.IV$subblock,
                                binID=tic.lu.C.16.comp.4b.bins.IV$binID,
                                time.elements=tic.lu.C.16.comp.4b.bins.IV$elements,
                                time.min=tic.lu.C.16.comp.4b.bins.IV$minimum,
                                time.avg=tic.lu.C.16.comp.4b.bins.IV$average,
                                time.max=tic.lu.C.16.comp.4b.bins.IV$maximum,
                                inst.elements=tic.lu.C.16.comp.4c.bins.IV$elements,
                                inst.min=tic.lu.C.16.comp.4c.bins.IV$minimum,
                                inst.avg=tic.lu.C.16.comp.4c.bins.IV$average,
                                inst.max=tic.lu.C.16.comp.4c.bins.IV$maximum)

d.C.16.4b.4c.bins.IV<-d.C.16.4b.4c.bins.IV[!(d.C.16.4b.4c.bins.IV$time.elements==0 & d.C.16.4b.4c.bins.IV$inst.elements==0),]

d.C.16.4b.4c.bins.V<-data.frame(eventID=tic.lu.C.16.comp.4b.bins.V$eventID,
                                subblock=tic.lu.C.16.comp.4b.bins.V$subblock,
                                binID=tic.lu.C.16.comp.4b.bins.V$binID,
                                time.elements=tic.lu.C.16.comp.4b.bins.V$elements,
                                time.min=tic.lu.C.16.comp.4b.bins.V$minimum,
                                time.avg=tic.lu.C.16.comp.4b.bins.V$average,
                                time.max=tic.lu.C.16.comp.4b.bins.V$maximum,
                                inst.elements=tic.lu.C.16.comp.4c.bins.V$elements,
                                inst.min=tic.lu.C.16.comp.4c.bins.V$minimum,
                                inst.avg=tic.lu.C.16.comp.4c.bins.V$average,
                                inst.max=tic.lu.C.16.comp.4c.bins.V$maximum)

d.C.16.4b.4c.bins.V<-d.C.16.4b.4c.bins.V[!(d.C.16.4b.4c.bins.V$time.elements==0 & d.C.16.4b.4c.bins.V$inst.elements==0),]
```

```{r}
ggplot(d.C.16.4b.4c.bins.I, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=eventID)) + geom_point() + geom_linerange() + geom_errorbar(width=d.C.16.4b.4c.bins.I$inst.max-d.C.16.4b.4c.bins.I$inst.min)
```

