---
title: 'Rough Estimation of Instruction Rate '
author: "Anshul Gupta"
date: "28/06/2014"
output: html_document
---

## Motive
Calculate the instruction rate of execution using TIC traces.

## Overview
5 traces with TIC instrumentation of LU benchmark, class C and 16 processes were acquired on graphene cluster.  
Their **COMP 4b** and **COMP 4c** global average values and involved processes were parsed using the _scripts/Expand.java_ code with this format.  
See _org/analysis.org_

```{r Init}
setwd('..')
library(ggplot2)
dataset.tic.lu.B.8.comp.4b.I<-read.table("datasets/tic.lu.B.8.comp.4b.I", header=TRUE)
dataset.tic.lu.B.8.comp.4b.II<-read.table("datasets/tic.lu.B.8.comp.4b.II", header=TRUE)
dataset.tic.lu.B.8.comp.4b.III<-read.table("datasets/tic.lu.B.8.comp.4b.III", header=TRUE)
dataset.tic.lu.B.8.comp.4b.IV<-read.table("datasets/tic.lu.B.8.comp.4b.IV", header=TRUE)
dataset.tic.lu.B.8.comp.4b.V<-read.table("datasets/tic.lu.B.8.comp.4b.V", header=TRUE)
dataset.tic.lu.B.8.comp.4c.I<-read.table("datasets/tic.lu.B.8.comp.4c.I", header=TRUE)
dataset.tic.lu.B.8.comp.4c.II<-read.table("datasets/tic.lu.B.8.comp.4c.II", header=TRUE)
dataset.tic.lu.B.8.comp.4c.III<-read.table("datasets/tic.lu.B.8.comp.4c.III", header=TRUE)
dataset.tic.lu.B.8.comp.4c.IV<-read.table("datasets/tic.lu.B.8.comp.4c.IV", header=TRUE)
dataset.tic.lu.B.8.comp.4c.V<-read.table("datasets/tic.lu.B.8.comp.4c.V", header=TRUE)

dataset.tic.lu.B.16.comp.4b.I<-read.table("datasets/tic.lu.B.16.comp.4b.I", header=TRUE)
dataset.tic.lu.B.16.comp.4b.II<-read.table("datasets/tic.lu.B.16.comp.4b.II", header=TRUE)
dataset.tic.lu.B.16.comp.4b.III<-read.table("datasets/tic.lu.B.16.comp.4b.III", header=TRUE)
dataset.tic.lu.B.16.comp.4b.IV<-read.table("datasets/tic.lu.B.16.comp.4b.IV", header=TRUE)
dataset.tic.lu.B.16.comp.4b.V<-read.table("datasets/tic.lu.B.16.comp.4b.V", header=TRUE)
dataset.tic.lu.B.16.comp.4c.I<-read.table("datasets/tic.lu.B.16.comp.4c.I", header=TRUE)
dataset.tic.lu.B.16.comp.4c.II<-read.table("datasets/tic.lu.B.16.comp.4c.II", header=TRUE)
dataset.tic.lu.B.16.comp.4c.III<-read.table("datasets/tic.lu.B.16.comp.4c.III", header=TRUE)
dataset.tic.lu.B.16.comp.4c.IV<-read.table("datasets/tic.lu.B.16.comp.4c.IV", header=TRUE)
dataset.tic.lu.B.16.comp.4c.V<-read.table("datasets/tic.lu.B.16.comp.4c.V", header=TRUE)

dataset.tic.lu.C.8.comp.4b.I<-read.table("datasets/tic.lu.C.8.comp.4b.I", header=TRUE)
dataset.tic.lu.C.8.comp.4b.II<-read.table("datasets/tic.lu.C.8.comp.4b.II", header=TRUE)
dataset.tic.lu.C.8.comp.4b.III<-read.table("datasets/tic.lu.C.8.comp.4b.III", header=TRUE)
dataset.tic.lu.C.8.comp.4b.IV<-read.table("datasets/tic.lu.C.8.comp.4b.IV", header=TRUE)
dataset.tic.lu.C.8.comp.4b.V<-read.table("datasets/tic.lu.C.8.comp.4b.V", header=TRUE)
dataset.tic.lu.C.8.comp.4c.I<-read.table("datasets/tic.lu.C.8.comp.4c.I", header=TRUE)
dataset.tic.lu.C.8.comp.4c.II<-read.table("datasets/tic.lu.C.8.comp.4c.II", header=TRUE)
dataset.tic.lu.C.8.comp.4c.III<-read.table("datasets/tic.lu.C.8.comp.4c.III", header=TRUE)
dataset.tic.lu.C.8.comp.4c.IV<-read.table("datasets/tic.lu.C.8.comp.4c.IV", header=TRUE)
dataset.tic.lu.C.8.comp.4c.V<-read.table("datasets/tic.lu.C.8.comp.4c.V", header=TRUE)

dataset.tic.lu.C.16.comp.4b.I<-read.table("datasets/tic.lu.C.16.comp.4b.I", header=TRUE)
dataset.tic.lu.C.16.comp.4b.II<-read.table("datasets/tic.lu.C.16.comp.4b.II", header=TRUE)
dataset.tic.lu.C.16.comp.4b.III<-read.table("datasets/tic.lu.C.16.comp.4b.III", header=TRUE)
dataset.tic.lu.C.16.comp.4b.IV<-read.table("datasets/tic.lu.C.16.comp.4b.IV", header=TRUE)
dataset.tic.lu.C.16.comp.4b.V<-read.table("datasets/tic.lu.C.16.comp.4b.V", header=TRUE)
dataset.tic.lu.C.16.comp.4c.I<-read.table("datasets/tic.lu.C.16.comp.4c.I", header=TRUE)
dataset.tic.lu.C.16.comp.4c.II<-read.table("datasets/tic.lu.C.16.comp.4c.II", header=TRUE)
dataset.tic.lu.C.16.comp.4c.III<-read.table("datasets/tic.lu.C.16.comp.4c.III", header=TRUE)
dataset.tic.lu.C.16.comp.4c.IV<-read.table("datasets/tic.lu.C.16.comp.4c.IV", header=TRUE)
dataset.tic.lu.C.16.comp.4c.V<-read.table("datasets/tic.lu.C.16.comp.4c.V", header=TRUE)
```

The variables are named as `d.<A>.<B>.4b.4c.<X>`,  
where `<X>` is the TIC dataset,   
`<A>` is the class,  
and `<B>` is the number of processes.  
Each `d.<A>.<B>.4b.4c.<X>` has 6 fields:

* eventID = Event ID
* opcode = Opcode of the event
* subblock = Subblock ID of the event
* events = Number of elements involved in the event
* COMP.4b.avg = Average of COMP 4b
* COMP.4c.avg = Average of COMP 4c

```{r Read datasets}
d.B.8.4b.4c.I<-cbind(dataset.tic.lu.B.8.comp.4b.I[,1:4], dataset.tic.lu.B.8.comp.4b.I$avg/1e6, dataset.tic.lu.B.8.comp.4c.I$avg*1e3)
d.B.8.4b.4c.II<-cbind(dataset.tic.lu.B.8.comp.4b.II[,1:4], dataset.tic.lu.B.8.comp.4b.II$avg/1e6, dataset.tic.lu.B.8.comp.4c.II$avg*1e3)
d.B.8.4b.4c.III<-cbind(dataset.tic.lu.B.8.comp.4b.III[,1:4], dataset.tic.lu.B.8.comp.4b.III$avg/1e6, dataset.tic.lu.B.8.comp.4c.III$avg*1e3)
d.B.8.4b.4c.IV<-cbind(dataset.tic.lu.B.8.comp.4b.IV[,1:4], dataset.tic.lu.B.8.comp.4b.IV$avg/1e6, dataset.tic.lu.B.8.comp.4c.IV$avg*1e3)
d.B.8.4b.4c.V<-cbind(dataset.tic.lu.B.8.comp.4b.V[,1:4], dataset.tic.lu.B.8.comp.4b.V$avg/1e6, dataset.tic.lu.B.8.comp.4c.V$avg*1e3)

colnames(d.B.8.4b.4c.I)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.B.8.4b.4c.II)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.B.8.4b.4c.III)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.B.8.4b.4c.IV)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.B.8.4b.4c.V)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")

d.B.16.4b.4c.I<-cbind(dataset.tic.lu.B.16.comp.4b.I[,1:4], dataset.tic.lu.B.16.comp.4b.I$avg/1e6, dataset.tic.lu.B.16.comp.4c.I$avg*1e3)
d.B.16.4b.4c.II<-cbind(dataset.tic.lu.B.16.comp.4b.II[,1:4], dataset.tic.lu.B.16.comp.4b.II$avg/1e6, dataset.tic.lu.B.16.comp.4c.II$avg*1e3)
d.B.16.4b.4c.III<-cbind(dataset.tic.lu.B.16.comp.4b.III[,1:4], dataset.tic.lu.B.16.comp.4b.III$avg/1e6, dataset.tic.lu.B.16.comp.4c.III$avg*1e3)
d.B.16.4b.4c.IV<-cbind(dataset.tic.lu.B.16.comp.4b.IV[,1:4], dataset.tic.lu.B.16.comp.4b.IV$avg/1e6, dataset.tic.lu.B.16.comp.4c.IV$avg*1e3)
d.B.16.4b.4c.V<-cbind(dataset.tic.lu.B.16.comp.4b.V[,1:4], dataset.tic.lu.B.16.comp.4b.V$avg/1e6, dataset.tic.lu.B.16.comp.4c.V$avg*1e3)

colnames(d.B.16.4b.4c.I)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.B.16.4b.4c.II)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.B.16.4b.4c.III)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.B.16.4b.4c.IV)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.B.16.4b.4c.V)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")

d.C.8.4b.4c.I<-cbind(dataset.tic.lu.C.8.comp.4b.I[,1:4], dataset.tic.lu.C.8.comp.4b.I$avg/1e6, dataset.tic.lu.C.8.comp.4c.I$avg*1e3)
d.C.8.4b.4c.II<-cbind(dataset.tic.lu.C.8.comp.4b.II[,1:4], dataset.tic.lu.C.8.comp.4b.II$avg/1e6, dataset.tic.lu.C.8.comp.4c.II$avg*1e3)
d.C.8.4b.4c.III<-cbind(dataset.tic.lu.C.8.comp.4b.III[,1:4], dataset.tic.lu.C.8.comp.4b.III$avg/1e6, dataset.tic.lu.C.8.comp.4c.III$avg*1e3)
d.C.8.4b.4c.IV<-cbind(dataset.tic.lu.C.8.comp.4b.IV[,1:4], dataset.tic.lu.C.8.comp.4b.IV$avg/1e6, dataset.tic.lu.C.8.comp.4c.IV$avg*1e3)
d.C.8.4b.4c.V<-cbind(dataset.tic.lu.C.8.comp.4b.V[,1:4], dataset.tic.lu.C.8.comp.4b.V$avg/1e6, dataset.tic.lu.C.8.comp.4c.V$avg*1e3)

colnames(d.C.8.4b.4c.I)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.C.8.4b.4c.II)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.C.8.4b.4c.III)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.C.8.4b.4c.IV)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.C.8.4b.4c.V)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")

d.C.16.4b.4c.I<-cbind(dataset.tic.lu.C.16.comp.4b.I[,1:4], dataset.tic.lu.C.16.comp.4b.I$avg/1e6, dataset.tic.lu.C.16.comp.4c.I$avg*1e3)
d.C.16.4b.4c.II<-cbind(dataset.tic.lu.C.16.comp.4b.II[,1:4], dataset.tic.lu.C.16.comp.4b.II$avg/1e6, dataset.tic.lu.C.16.comp.4c.II$avg*1e3)
d.C.16.4b.4c.III<-cbind(dataset.tic.lu.C.16.comp.4b.III[,1:4], dataset.tic.lu.C.16.comp.4b.III$avg/1e6, dataset.tic.lu.C.16.comp.4c.III$avg*1e3)
d.C.16.4b.4c.IV<-cbind(dataset.tic.lu.C.16.comp.4b.IV[,1:4], dataset.tic.lu.C.16.comp.4b.IV$avg/1e6, dataset.tic.lu.C.16.comp.4c.IV$avg*1e3)
d.C.16.4b.4c.V<-cbind(dataset.tic.lu.C.16.comp.4b.V[,1:4], dataset.tic.lu.C.16.comp.4b.V$avg/1e6, dataset.tic.lu.C.16.comp.4c.V$avg*1e3)

colnames(d.C.16.4b.4c.I)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.C.16.4b.4c.II)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.C.16.4b.4c.III)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.C.16.4b.4c.IV)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
colnames(d.C.16.4b.4c.V)[5:6]<-c("COMP.4b.avg", "COMP.4c.avg")
```

### Get the average instruction rate
Having COMP 4b averages and COMP 4c averages, instruction rate is calculated by:   
`instruction rate = mean(COMP.4c.average / COMP.4b.average)`

**Instruction Rate for dataset.tic.B.8**

```{r Instruction Rate Dataset B 8}
inst.rate.B.8<-c(mean(d.B.8.4b.4c.I$COMP.4c.avg/d.B.8.4b.4c.I$COMP.4b.avg),
     mean(d.B.8.4b.4c.II$COMP.4c.avg/d.B.8.4b.4c.II$COMP.4b.avg),
     mean(d.B.8.4b.4c.III$COMP.4c.avg/d.B.8.4b.4c.III$COMP.4b.avg),
     mean(d.B.8.4b.4c.IV$COMP.4c.avg/d.B.8.4b.4c.IV$COMP.4b.avg),
     mean(d.B.8.4b.4c.V$COMP.4c.avg/d.B.8.4b.4c.V$COMP.4b.avg))

names(inst.rate.B.8)<-c('dataset1','dataset2','dataset3','dataset4','dataset5')
print(inst.rate.B.8)
```

**Instruction Rate for dataset.tic.B.16**

```{r Instruction Rate Dataset B 16}
inst.rate.B.16<-c(mean(d.B.16.4b.4c.I$COMP.4c.avg/d.B.16.4b.4c.I$COMP.4b.avg),
     mean(d.B.16.4b.4c.II$COMP.4c.avg/d.B.16.4b.4c.II$COMP.4b.avg),
     mean(d.B.16.4b.4c.III$COMP.4c.avg/d.B.16.4b.4c.III$COMP.4b.avg),
     mean(d.B.16.4b.4c.IV$COMP.4c.avg/d.B.16.4b.4c.IV$COMP.4b.avg),
     mean(d.B.16.4b.4c.V$COMP.4c.avg/d.B.16.4b.4c.V$COMP.4b.avg))

names(inst.rate.B.16)<-c('dataset1','dataset2','dataset3','dataset4','dataset5')
print(inst.rate.B.16)
```

**Instruction Rate for dataset.tic.C.8**

```{r Instruction Rate Dataset C 8}
inst.rate.C.8<-c(mean(d.C.8.4b.4c.I$COMP.4c.avg/d.C.8.4b.4c.I$COMP.4b.avg),
     mean(d.C.8.4b.4c.II$COMP.4c.avg/d.C.8.4b.4c.II$COMP.4b.avg),
     mean(d.C.8.4b.4c.III$COMP.4c.avg/d.C.8.4b.4c.III$COMP.4b.avg),
     mean(d.C.8.4b.4c.IV$COMP.4c.avg/d.C.8.4b.4c.IV$COMP.4b.avg),
     mean(d.C.8.4b.4c.V$COMP.4c.avg/d.C.8.4b.4c.V$COMP.4b.avg))

names(inst.rate.C.8)<-c('dataset1','dataset2','dataset3','dataset4','dataset5')
print(inst.rate.C.8)
```

**Instruction Rate for dataset.tic.C.16**

```{r Instruction Rate Dataset C 16}
inst.rate.C.16<-c(mean(d.C.16.4b.4c.I$COMP.4c.avg/d.C.16.4b.4c.I$COMP.4b.avg),
     mean(d.C.16.4b.4c.II$COMP.4c.avg/d.C.16.4b.4c.II$COMP.4b.avg),
     mean(d.C.16.4b.4c.III$COMP.4c.avg/d.C.16.4b.4c.III$COMP.4b.avg),
     mean(d.C.16.4b.4c.IV$COMP.4c.avg/d.C.16.4b.4c.IV$COMP.4b.avg),
     mean(d.C.16.4b.4c.V$COMP.4c.avg/d.C.16.4b.4c.V$COMP.4b.avg))

names(inst.rate.C.16)<-c('dataset1','dataset2','dataset3','dataset4','dataset5')
print(inst.rate.C.16)
```

## Plots
On x-axis, we have the eventID_subblock.  
On y-axis, we have the Instruction Rate (COMP.4c.avg/COMP.4b.avg).  
The size of each point represents the number of elements involved in the current event_subblock.  
Color represents the average number of instructions (COMP.4c.avg).  

**Dataset.tic.B.8.I**  

```{r Events vs Instruction Rate Dataset B 8 1}
ggplot(d.B.8.4b.4c.I, aes(x=1:nrow(d.B.8.4b.4c.I),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.B.8[1])
```

**Dataset.tic.B.8.II**  

```{r Events vs Instruction Rate Dataset B 8 2}
ggplot(d.B.8.4b.4c.II, aes(x=1:nrow(d.B.8.4b.4c.II),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.B.8[2])
```

**Dataset.tic.B.8.III**  

```{r Events vs Instruction Rate Dataset B 8 3}
ggplot(d.B.8.4b.4c.III, aes(x=1:nrow(d.B.8.4b.4c.III),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.B.8[3])
```

**Dataset.tic.B.8.IV**  

```{r Events vs Instruction Rate Dataset B 8 4}
ggplot(d.B.8.4b.4c.IV, aes(x=1:nrow(d.B.8.4b.4c.IV),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.B.8[4])
```

**Dataset.tic.B.8.V**  

```{r Events vs Instruction Rate Dataset B 8 5}
ggplot(d.B.8.4b.4c.V, aes(x=1:nrow(d.B.8.4b.4c.V),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.B.8[5])
```

**Dataset.tic.B.16.I**  

```{r Events vs Instruction Rate Dataset B 16 1}
ggplot(d.B.16.4b.4c.I, aes(x=1:nrow(d.B.16.4b.4c.I),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.B.16[1])
```

**Dataset.tic.B.16.II**  

```{r Events vs Instruction Rate Dataset B 16 2}
ggplot(d.B.16.4b.4c.II, aes(x=1:nrow(d.B.16.4b.4c.II),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.B.16[2])
```

**Dataset.tic.B.16.III**  

```{r Events vs Instruction Rate Dataset B 16 3}
ggplot(d.B.16.4b.4c.III, aes(x=1:nrow(d.B.16.4b.4c.III),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.B.16[3])
```

**Dataset.tic.B.16.IV**  

```{r Events vs Instruction Rate Dataset B 16 4}
ggplot(d.B.16.4b.4c.IV, aes(x=1:nrow(d.B.16.4b.4c.IV),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.B.16[4])
```

**Dataset.tic.B.16.V**  

```{r Events vs Instruction Rate Dataset B 16 5}
ggplot(d.B.16.4b.4c.V, aes(x=1:nrow(d.B.16.4b.4c.V),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.B.16[5])
```

**Dataset.tic.C.8.I**  

```{r Events vs Instruction Rate Dataset C 8 1}
ggplot(d.C.8.4b.4c.I, aes(x=1:nrow(d.C.8.4b.4c.I),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.C.8[1])
```

**Dataset.tic.C.8.II**  

```{r Events vs Instruction Rate Dataset C 8 2}
ggplot(d.C.8.4b.4c.II, aes(x=1:nrow(d.C.8.4b.4c.II),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.C.8[2])
```

**Dataset.tic.C.8.III**  

```{r Events vs Instruction Rate Dataset C 8 3}
ggplot(d.C.8.4b.4c.III, aes(x=1:nrow(d.C.8.4b.4c.III),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.C.8[3])
```

**Dataset.tic.C.8.IV**  

```{r Events vs Instruction Rate Dataset C 8 4}
ggplot(d.C.8.4b.4c.IV, aes(x=1:nrow(d.C.8.4b.4c.IV),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.C.8[4])
```

**Dataset.tic.C.8.V**  

```{r Events vs Instruction Rate Dataset C 8 5}
ggplot(d.C.8.4b.4c.V, aes(x=1:nrow(d.C.8.4b.4c.V),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.C.8[5])
```

**Dataset.tic.C.16.I**  

```{r Events vs Instruction Rate Dataset C 16 1}
ggplot(d.C.16.4b.4c.I, aes(x=1:nrow(d.C.16.4b.4c.I),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.C.16[1])
```

**Dataset.tic.C.16.II**  

```{r Events vs Instruction Rate Dataset C 16 2}
ggplot(d.C.16.4b.4c.II, aes(x=1:nrow(d.C.16.4b.4c.II),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.C.16[2])
```

**Dataset.tic.C.16.III**  

```{r Events vs Instruction Rate Dataset C 16 3}
ggplot(d.C.16.4b.4c.III, aes(x=1:nrow(d.C.16.4b.4c.III),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.C.16[3])
```

**Dataset.tic.C.16.IV**  

```{r Events vs Instruction Rate Dataset C 16 4}
ggplot(d.C.16.4b.4c.IV, aes(x=1:nrow(d.C.16.4b.4c.IV),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.C.16[4])
```

**Dataset.tic.C.16.V**  

```{r Events vs Instruction Rate Dataset C 16 5}
ggplot(d.C.16.4b.4c.V, aes(x=1:nrow(d.C.16.4b.4c.V),
                      y=COMP.4c.avg/COMP.4b.avg,
                      color=COMP.4c.avg,
                      size=events)) +
  geom_point() + xlab("Event") + ylab("Instruction Rate") +
  geom_hline(yintercept=inst.rate.C.16[5])
```


## Results
Instruction rate for **Class B, 8 processes** is around **3.5e9 Instructions per sec**.  
Instruction rate for **Class B, 16 processes** is around **3.4e9 Instructions per sec**.  
Instruction rate for **Class C, 8 processes** is around **3.4e9 Instructions per sec**.  
Instruction rate for **Class C, 16 processes** is around **3.4e9 Instructions per sec**.  

## Conclusions
It is clear from the plots that the executions are quite stable as CPU bursts on each execution occur at same places.

