---
title: "Variablity"
author: "Anshul Gupta"
date: "06/07/2014"
output: html_document
---

## Motive
Plot the variablity of execution in TIC traces.

## Overview
5 traces with TIC instrumentation of LU benchmark, class C and 16 processes were acquired on graphene cluster.  
Their **COMP 4b** and **COMP 4c** global average values and involved processes were parsed using the _scripts/Expand.java_ code with this format.  
See _org/analysis.org_

The global values in the traces are modified according to 10% threshold of events in indivudial bins.

```{r Init}
setwd("..")
library(ggplot2)
dataset.tic.lu.B.8.comp.4c.I<-read.table("datasets/tic.lu.B.8.comp.4c.processed.I", header=TRUE)
dataset.tic.lu.B.8.comp.4c.II<-read.table("datasets/tic.lu.B.8.comp.4c.processed.II", header=TRUE)
dataset.tic.lu.B.8.comp.4c.III<-read.table("datasets/tic.lu.B.8.comp.4c.processed.III", header=TRUE)
dataset.tic.lu.B.8.comp.4c.IV<-read.table("datasets/tic.lu.B.8.comp.4c.processed.IV", header=TRUE)
dataset.tic.lu.B.8.comp.4c.V<-read.table("datasets/tic.lu.B.8.comp.4c.processed.V", header=TRUE)

dataset.tic.lu.B.8.comp.4b.I<-read.table("datasets/tic.lu.B.8.comp.4b.processed.I", header=TRUE)
dataset.tic.lu.B.8.comp.4b.II<-read.table("datasets/tic.lu.B.8.comp.4b.processed.II", header=TRUE)
dataset.tic.lu.B.8.comp.4b.III<-read.table("datasets/tic.lu.B.8.comp.4b.processed.III", header=TRUE)
dataset.tic.lu.B.8.comp.4b.IV<-read.table("datasets/tic.lu.B.8.comp.4b.processed.IV", header=TRUE)
dataset.tic.lu.B.8.comp.4b.V<-read.table("datasets/tic.lu.B.8.comp.4b.processed.V", header=TRUE)

dataset.tic.lu.B.16.comp.4c.I<-read.table("datasets/tic.lu.B.16.comp.4c.processed.I", header=TRUE)
dataset.tic.lu.B.16.comp.4c.II<-read.table("datasets/tic.lu.B.16.comp.4c.processed.II", header=TRUE)
dataset.tic.lu.B.16.comp.4c.III<-read.table("datasets/tic.lu.B.16.comp.4c.processed.III", header=TRUE)
dataset.tic.lu.B.16.comp.4c.IV<-read.table("datasets/tic.lu.B.16.comp.4c.processed.IV", header=TRUE)
dataset.tic.lu.B.16.comp.4c.V<-read.table("datasets/tic.lu.B.16.comp.4c.processed.V", header=TRUE)

dataset.tic.lu.B.16.comp.4b.I<-read.table("datasets/tic.lu.B.16.comp.4b.processed.I", header=TRUE)
dataset.tic.lu.B.16.comp.4b.II<-read.table("datasets/tic.lu.B.16.comp.4b.processed.II", header=TRUE)
dataset.tic.lu.B.16.comp.4b.III<-read.table("datasets/tic.lu.B.16.comp.4b.processed.III", header=TRUE)
dataset.tic.lu.B.16.comp.4b.IV<-read.table("datasets/tic.lu.B.16.comp.4b.processed.IV", header=TRUE)
dataset.tic.lu.B.16.comp.4b.V<-read.table("datasets/tic.lu.B.16.comp.4b.processed.V", header=TRUE)

dataset.tic.lu.C.8.comp.4c.I<-read.table("datasets/tic.lu.C.8.comp.4c.processed.I", header=TRUE)
dataset.tic.lu.C.8.comp.4c.II<-read.table("datasets/tic.lu.C.8.comp.4c.processed.II", header=TRUE)
dataset.tic.lu.C.8.comp.4c.III<-read.table("datasets/tic.lu.C.8.comp.4c.processed.III", header=TRUE)
dataset.tic.lu.C.8.comp.4c.IV<-read.table("datasets/tic.lu.C.8.comp.4c.processed.IV", header=TRUE)
dataset.tic.lu.C.8.comp.4c.V<-read.table("datasets/tic.lu.C.8.comp.4c.processed.V", header=TRUE)

dataset.tic.lu.C.8.comp.4b.I<-read.table("datasets/tic.lu.C.8.comp.4b.processed.I", header=TRUE)
dataset.tic.lu.C.8.comp.4b.II<-read.table("datasets/tic.lu.C.8.comp.4b.processed.II", header=TRUE)
dataset.tic.lu.C.8.comp.4b.III<-read.table("datasets/tic.lu.C.8.comp.4b.processed.III", header=TRUE)
dataset.tic.lu.C.8.comp.4b.IV<-read.table("datasets/tic.lu.C.8.comp.4b.processed.IV", header=TRUE)
dataset.tic.lu.C.8.comp.4b.V<-read.table("datasets/tic.lu.C.8.comp.4b.processed.V", header=TRUE)

dataset.tic.lu.C.16.comp.4c.I<-read.table("datasets/tic.lu.C.16.comp.4c.processed.I", header=TRUE)
dataset.tic.lu.C.16.comp.4c.II<-read.table("datasets/tic.lu.C.16.comp.4c.processed.II", header=TRUE)
dataset.tic.lu.C.16.comp.4c.III<-read.table("datasets/tic.lu.C.16.comp.4c.processed.III", header=TRUE)
dataset.tic.lu.C.16.comp.4c.IV<-read.table("datasets/tic.lu.C.16.comp.4c.processed.IV", header=TRUE)
dataset.tic.lu.C.16.comp.4c.V<-read.table("datasets/tic.lu.C.16.comp.4c.processed.V", header=TRUE)

dataset.tic.lu.C.16.comp.4b.I<-read.table("datasets/tic.lu.C.16.comp.4b.processed.I", header=TRUE)
dataset.tic.lu.C.16.comp.4b.II<-read.table("datasets/tic.lu.C.16.comp.4b.processed.II", header=TRUE)
dataset.tic.lu.C.16.comp.4b.III<-read.table("datasets/tic.lu.C.16.comp.4b.processed.III", header=TRUE)
dataset.tic.lu.C.16.comp.4b.IV<-read.table("datasets/tic.lu.C.16.comp.4b.processed.IV", header=TRUE)
dataset.tic.lu.C.16.comp.4b.V<-read.table("datasets/tic.lu.C.16.comp.4b.processed.V", header=TRUE)
```

The variables are named as `d.<A>.<B>.4b.4c.<X>`,  
where `<X>` is the TIC dataset,   
`<A>` is the class,  
and `<B>` is the number of processes.  
Each `d.<A>.<B>.4b.4c.<X>` has 6 fields:

* elements = Number of elements
* time.avg = Average time after processing
* subblock = Subblock ID of the event
* events = Number of elements involved in the event
* COMP.4b.avg = Average of COMP 4b
* COMP.4c.avg = Average of COMP 4c

```{r Read datasets}
d.B.8.4b.4c.I<-data.frame(elements=dataset.tic.lu.B.8.comp.4b.I$events,
                           time.avg=dataset.tic.lu.B.8.comp.4b.I$avg/1e6,
                           time.min=dataset.tic.lu.B.8.comp.4b.I$min/1e6,
                           time.max=dataset.tic.lu.B.8.comp.4b.I$max/1e6,
                           inst.avg=dataset.tic.lu.B.8.comp.4c.I$avg*1000,
                           inst.min=dataset.tic.lu.B.8.comp.4c.I$min*1000,
                           inst.max=dataset.tic.lu.B.8.comp.4c.I$max*1000)

d.B.8.4b.4c.II<-data.frame(elements=dataset.tic.lu.B.8.comp.4b.II$events,
                           time.avg=dataset.tic.lu.B.8.comp.4b.II$avg/1e6,
                           time.min=dataset.tic.lu.B.8.comp.4b.II$min/1e6,
                           time.max=dataset.tic.lu.B.8.comp.4b.II$max/1e6,
                           inst.avg=dataset.tic.lu.B.8.comp.4c.II$avg*1000,
                           inst.min=dataset.tic.lu.B.8.comp.4c.II$min*1000,
                           inst.max=dataset.tic.lu.B.8.comp.4c.II$max*1000)

d.B.8.4b.4c.III<-data.frame(elements=dataset.tic.lu.B.8.comp.4b.III$events,
                           time.avg=dataset.tic.lu.B.8.comp.4b.III$avg/1e6,
                           time.min=dataset.tic.lu.B.8.comp.4b.III$min/1e6,
                           time.max=dataset.tic.lu.B.8.comp.4b.III$max/1e6,
                           inst.avg=dataset.tic.lu.B.8.comp.4c.III$avg*1000,
                           inst.min=dataset.tic.lu.B.8.comp.4c.III$min*1000,
                           inst.max=dataset.tic.lu.B.8.comp.4c.III$max*1000)

d.B.8.4b.4c.IV<-data.frame(elements=dataset.tic.lu.B.8.comp.4b.IV$events,
                           time.avg=dataset.tic.lu.B.8.comp.4b.IV$avg/1e6,
                           time.min=dataset.tic.lu.B.8.comp.4b.IV$min/1e6,
                           time.max=dataset.tic.lu.B.8.comp.4b.IV$max/1e6,
                           inst.avg=dataset.tic.lu.B.8.comp.4c.IV$avg*1000,
                           inst.min=dataset.tic.lu.B.8.comp.4c.IV$min*1000,
                           inst.max=dataset.tic.lu.B.8.comp.4c.IV$max*1000)

d.B.8.4b.4c.V<-data.frame(elements=dataset.tic.lu.B.8.comp.4b.V$events,
                           time.avg=dataset.tic.lu.B.8.comp.4b.V$avg/1e6,
                           time.min=dataset.tic.lu.B.8.comp.4b.V$min/1e6,
                           time.max=dataset.tic.lu.B.8.comp.4b.V$max/1e6,
                           inst.avg=dataset.tic.lu.B.8.comp.4c.V$avg*1000,
                           inst.min=dataset.tic.lu.B.8.comp.4c.V$min*1000,
                           inst.max=dataset.tic.lu.B.8.comp.4c.V$max*1000)
                           
d.B.16.4b.4c.I<-data.frame(elements=dataset.tic.lu.B.16.comp.4b.I$events,
                           time.avg=dataset.tic.lu.B.16.comp.4b.I$avg/1e6,
                           time.min=dataset.tic.lu.B.16.comp.4b.I$min/1e6,
                           time.max=dataset.tic.lu.B.16.comp.4b.I$max/1e6,
                           inst.avg=dataset.tic.lu.B.16.comp.4c.I$avg*1000,
                           inst.min=dataset.tic.lu.B.16.comp.4c.I$min*1000,
                           inst.max=dataset.tic.lu.B.16.comp.4c.I$max*1000)

d.B.16.4b.4c.II<-data.frame(elements=dataset.tic.lu.B.16.comp.4b.II$events,
                           time.avg=dataset.tic.lu.B.16.comp.4b.II$avg/1e6,
                           time.min=dataset.tic.lu.B.16.comp.4b.II$min/1e6,
                           time.max=dataset.tic.lu.B.16.comp.4b.II$max/1e6,
                           inst.avg=dataset.tic.lu.B.16.comp.4c.II$avg*1000,
                           inst.min=dataset.tic.lu.B.16.comp.4c.II$min*1000,
                           inst.max=dataset.tic.lu.B.16.comp.4c.II$max*1000)

d.B.16.4b.4c.III<-data.frame(elements=dataset.tic.lu.B.16.comp.4b.III$events,
                           time.avg=dataset.tic.lu.B.16.comp.4b.III$avg/1e6,
                           time.min=dataset.tic.lu.B.16.comp.4b.III$min/1e6,
                           time.max=dataset.tic.lu.B.16.comp.4b.III$max/1e6,
                           inst.avg=dataset.tic.lu.B.16.comp.4c.III$avg*1000,
                           inst.min=dataset.tic.lu.B.16.comp.4c.III$min*1000,
                           inst.max=dataset.tic.lu.B.16.comp.4c.III$max*1000)

d.B.16.4b.4c.IV<-data.frame(elements=dataset.tic.lu.B.16.comp.4b.IV$events,
                           time.avg=dataset.tic.lu.B.16.comp.4b.IV$avg/1e6,
                           time.min=dataset.tic.lu.B.16.comp.4b.IV$min/1e6,
                           time.max=dataset.tic.lu.B.16.comp.4b.IV$max/1e6,
                           inst.avg=dataset.tic.lu.B.16.comp.4c.IV$avg*1000,
                           inst.min=dataset.tic.lu.B.16.comp.4c.IV$min*1000,
                           inst.max=dataset.tic.lu.B.16.comp.4c.IV$max*1000)

d.B.16.4b.4c.V<-data.frame(elements=dataset.tic.lu.B.16.comp.4b.V$events,
                           time.avg=dataset.tic.lu.B.16.comp.4b.V$avg/1e6,
                           time.min=dataset.tic.lu.B.16.comp.4b.V$min/1e6,
                           time.max=dataset.tic.lu.B.16.comp.4b.V$max/1e6,
                           inst.avg=dataset.tic.lu.B.16.comp.4c.V$avg*1000,
                           inst.min=dataset.tic.lu.B.16.comp.4c.V$min*1000,
                           inst.max=dataset.tic.lu.B.16.comp.4c.V$max*1000)
                           
d.C.8.4b.4c.I<-data.frame(elements=dataset.tic.lu.C.8.comp.4b.I$events,
                           time.avg=dataset.tic.lu.C.8.comp.4b.I$avg/1e6,
                           time.min=dataset.tic.lu.C.8.comp.4b.I$min/1e6,
                           time.max=dataset.tic.lu.C.8.comp.4b.I$max/1e6,
                           inst.avg=dataset.tic.lu.C.8.comp.4c.I$avg*1000,
                           inst.min=dataset.tic.lu.C.8.comp.4c.I$min*1000,
                           inst.max=dataset.tic.lu.C.8.comp.4c.I$max*1000)

d.C.8.4b.4c.II<-data.frame(elements=dataset.tic.lu.C.8.comp.4b.II$events,
                           time.avg=dataset.tic.lu.C.8.comp.4b.II$avg/1e6,
                           time.min=dataset.tic.lu.C.8.comp.4b.II$min/1e6,
                           time.max=dataset.tic.lu.C.8.comp.4b.II$max/1e6,
                           inst.avg=dataset.tic.lu.C.8.comp.4c.II$avg*1000,
                           inst.min=dataset.tic.lu.C.8.comp.4c.II$min*1000,
                           inst.max=dataset.tic.lu.C.8.comp.4c.II$max*1000)

d.C.8.4b.4c.III<-data.frame(elements=dataset.tic.lu.C.8.comp.4b.III$events,
                           time.avg=dataset.tic.lu.C.8.comp.4b.III$avg/1e6,
                           time.min=dataset.tic.lu.C.8.comp.4b.III$min/1e6,
                           time.max=dataset.tic.lu.C.8.comp.4b.III$max/1e6,
                           inst.avg=dataset.tic.lu.C.8.comp.4c.III$avg*1000,
                           inst.min=dataset.tic.lu.C.8.comp.4c.III$min*1000,
                           inst.max=dataset.tic.lu.C.8.comp.4c.III$max*1000)

d.C.8.4b.4c.IV<-data.frame(elements=dataset.tic.lu.C.8.comp.4b.IV$events,
                           time.avg=dataset.tic.lu.C.8.comp.4b.IV$avg/1e6,
                           time.min=dataset.tic.lu.C.8.comp.4b.IV$min/1e6,
                           time.max=dataset.tic.lu.C.8.comp.4b.IV$max/1e6,
                           inst.avg=dataset.tic.lu.C.8.comp.4c.IV$avg*1000,
                           inst.min=dataset.tic.lu.C.8.comp.4c.IV$min*1000,
                           inst.max=dataset.tic.lu.C.8.comp.4c.IV$max*1000)

d.C.8.4b.4c.V<-data.frame(elements=dataset.tic.lu.C.8.comp.4b.V$events,
                           time.avg=dataset.tic.lu.C.8.comp.4b.V$avg/1e6,
                           time.min=dataset.tic.lu.C.8.comp.4b.V$min/1e6,
                           time.max=dataset.tic.lu.C.8.comp.4b.V$max/1e6,
                           inst.avg=dataset.tic.lu.C.8.comp.4c.V$avg*1000,
                           inst.min=dataset.tic.lu.C.8.comp.4c.V$min*1000,
                           inst.max=dataset.tic.lu.C.8.comp.4c.V$max*1000)
                           
d.C.16.4b.4c.I<-data.frame(elements=dataset.tic.lu.C.16.comp.4b.I$events,
                           time.avg=dataset.tic.lu.C.16.comp.4b.I$avg/1e6,
                           time.min=dataset.tic.lu.C.16.comp.4b.I$min/1e6,
                           time.max=dataset.tic.lu.C.16.comp.4b.I$max/1e6,
                           inst.avg=dataset.tic.lu.C.16.comp.4c.I$avg*1000,
                           inst.min=dataset.tic.lu.C.16.comp.4c.I$min*1000,
                           inst.max=dataset.tic.lu.C.16.comp.4c.I$max*1000)

d.C.16.4b.4c.II<-data.frame(elements=dataset.tic.lu.C.16.comp.4b.II$events,
                           time.avg=dataset.tic.lu.C.16.comp.4b.II$avg/1e6,
                           time.min=dataset.tic.lu.C.16.comp.4b.II$min/1e6,
                           time.max=dataset.tic.lu.C.16.comp.4b.II$max/1e6,
                           inst.avg=dataset.tic.lu.C.16.comp.4c.II$avg*1000,
                           inst.min=dataset.tic.lu.C.16.comp.4c.II$min*1000,
                           inst.max=dataset.tic.lu.C.16.comp.4c.II$max*1000)

d.C.16.4b.4c.III<-data.frame(elements=dataset.tic.lu.C.16.comp.4b.III$events,
                           time.avg=dataset.tic.lu.C.16.comp.4b.III$avg/1e6,
                           time.min=dataset.tic.lu.C.16.comp.4b.III$min/1e6,
                           time.max=dataset.tic.lu.C.16.comp.4b.III$max/1e6,
                           inst.avg=dataset.tic.lu.C.16.comp.4c.III$avg*1000,
                           inst.min=dataset.tic.lu.C.16.comp.4c.III$min*1000,
                           inst.max=dataset.tic.lu.C.16.comp.4c.III$max*1000)

d.C.16.4b.4c.IV<-data.frame(elements=dataset.tic.lu.C.16.comp.4b.IV$events,
                           time.avg=dataset.tic.lu.C.16.comp.4b.IV$avg/1e6,
                           time.min=dataset.tic.lu.C.16.comp.4b.IV$min/1e6,
                           time.max=dataset.tic.lu.C.16.comp.4b.IV$max/1e6,
                           inst.avg=dataset.tic.lu.C.16.comp.4c.IV$avg*1000,
                           inst.min=dataset.tic.lu.C.16.comp.4c.IV$min*1000,
                           inst.max=dataset.tic.lu.C.16.comp.4c.IV$max*1000)

d.C.16.4b.4c.V<-data.frame(elements=dataset.tic.lu.C.16.comp.4b.V$events,
                           time.avg=dataset.tic.lu.C.16.comp.4b.V$avg/1e6,
                           time.min=dataset.tic.lu.C.16.comp.4b.V$min/1e6,
                           time.max=dataset.tic.lu.C.16.comp.4b.V$max/1e6,
                           inst.avg=dataset.tic.lu.C.16.comp.4c.V$avg*1000,
                           inst.min=dataset.tic.lu.C.16.comp.4c.V$min*1000,
                           inst.max=dataset.tic.lu.C.16.comp.4c.V$max*1000)
```

## Plots
On x-axis, we have the Instructions.  
On y-axis, we have the Time (COMP.4c.avg/COMP.4b.avg).  
The color represents the number of elements involved in the current event_subblock.  

**Dataset.tic.B.8.Processed.I**  
```{r Events vs Instruction Rate Dataset B 8 Processed I}
ggplot(d.B.8.4b.4c.I, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.B.8.4b.4c.I$inst.max - d.B.8.4b.4c.I$inst.min) + scale_y_log10()
```

**Dataset.tic.B.8.Processed.II**  
```{r Events vs Instruction Rate Dataset B 8 Processed II}
ggplot(d.B.8.4b.4c.II, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.B.8.4b.4c.II$inst.max - d.B.8.4b.4c.II$inst.min) + scale_y_log10()
```

**Dataset.tic.B.8.Processed.III**  
```{r Events vs Instruction Rate Dataset B 8 Processed III}
ggplot(d.B.8.4b.4c.III, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.B.8.4b.4c.III$inst.max - d.B.8.4b.4c.III$inst.min) + scale_y_log10()
```

**Dataset.tic.B.8.Processed.I**  
```{r Events vs Instruction Rate Dataset B 8 Processed IV}
ggplot(d.B.8.4b.4c.IV, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.B.8.4b.4c.IV$inst.max - d.B.8.4b.4c.IV$inst.min) + scale_y_log10()
```

**Dataset.tic.B.8.Processed.V**  
```{r Events vs Instruction Rate Dataset B 8 Processed V}
ggplot(d.B.8.4b.4c.V, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.B.8.4b.4c.V$inst.max - d.B.8.4b.4c.V$inst.min) + scale_y_log10()
```

**Dataset.tic.B.16.Processed.I**  
```{r Events vs Instruction Rate Dataset B 16 Processed I}
ggplot(d.B.16.4b.4c.I, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.B.16.4b.4c.I$inst.max - d.B.16.4b.4c.I$inst.min) + scale_y_log10()
```

**Dataset.tic.B.16.Processed.II**  
```{r Events vs Instruction Rate Dataset B 16 Processed II}
ggplot(d.B.16.4b.4c.II, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.B.16.4b.4c.II$inst.max - d.B.16.4b.4c.II$inst.min) + scale_y_log10()
```

**Dataset.tic.B.16.Processed.III**  
```{r Events vs Instruction Rate Dataset B 16 Processed III}
ggplot(d.B.16.4b.4c.III, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.B.16.4b.4c.III$inst.max - d.B.16.4b.4c.III$inst.min) + scale_y_log10()
```

**Dataset.tic.B.16.Processed.I**  
```{r Events vs Instruction Rate Dataset B 16 Processed IV}
ggplot(d.B.16.4b.4c.IV, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.B.16.4b.4c.IV$inst.max - d.B.16.4b.4c.IV$inst.min) + scale_y_log10()
```

**Dataset.tic.B.16.Processed.V**  
```{r Events vs Instruction Rate Dataset B 16 Processed V}
ggplot(d.B.16.4b.4c.V, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.B.16.4b.4c.V$inst.max - d.B.16.4b.4c.V$inst.min) + scale_y_log10()
```

**Dataset.tic.C.8.Processed.I**  
```{r Events vs Instruction Rate Dataset C 8 Processed I}
ggplot(d.C.8.4b.4c.I, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.C.8.4b.4c.I$inst.max - d.C.8.4b.4c.I$inst.min) + scale_y_log10()
```

**Dataset.tic.C.8.Processed.II**  
```{r Events vs Instruction Rate Dataset C 8 Processed II}
ggplot(d.C.8.4b.4c.II, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.C.8.4b.4c.II$inst.max - d.C.8.4b.4c.II$inst.min) + scale_y_log10()
```

**Dataset.tic.C.8.Processed.III**  
```{r Events vs Instruction Rate Dataset C 8 Processed III}
ggplot(d.C.8.4b.4c.III, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.C.8.4b.4c.III$inst.max - d.C.8.4b.4c.III$inst.min) + scale_y_log10()
```

**Dataset.tic.C.8.Processed.IV**  
```{r Events vs Instruction Rate Dataset C 8 Processed IV}
ggplot(d.C.8.4b.4c.IV, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.C.8.4b.4c.IV$inst.max - d.C.8.4b.4c.IV$inst.min) + scale_y_log10()
```

**Dataset.tic.C.8.Processed.V**  
```{r Events vs Instruction Rate Dataset C 8 Processed V}
ggplot(d.C.8.4b.4c.V, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.C.8.4b.4c.V$inst.max - d.C.8.4b.4c.V$inst.min) + scale_y_log10()
```

**Dataset.tic.C.16.Processed.I**  
```{r Events vs Instruction Rate Dataset C 16 Processed I}
ggplot(d.C.16.4b.4c.I, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.C.16.4b.4c.I$inst.max - d.C.16.4b.4c.I$inst.min) + scale_y_log10()
```

**Dataset.tic.C.16.Processed.II**  
```{r Events vs Instruction Rate Dataset C 16 Processed II}
ggplot(d.C.16.4b.4c.II, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.C.16.4b.4c.II$inst.max - d.C.16.4b.4c.II$inst.min) + scale_y_log10()
```

**Dataset.tic.C.16.Processed.III**  
```{r Events vs Instruction Rate Dataset C 16 Processed III}
ggplot(d.C.16.4b.4c.III, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.C.16.4b.4c.III$inst.max - d.C.16.4b.4c.III$inst.min) + scale_y_log10()
```

**Dataset.tic.C.16.Processed.IV**  
```{r Events vs Instruction Rate Dataset C 16 Processed IV}
ggplot(d.C.16.4b.4c.IV, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.C.16.4b.4c.IV$inst.max - d.C.16.4b.4c.IV$inst.min) + scale_y_log10()
```

**Dataset.tic.C.16.Processed.V**  
```{r Events vs Instruction Rate Dataset C 16 Processed V}
ggplot(d.C.16.4b.4c.V, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=(elements))) + geom_point() + geom_linerange() + geom_errorbar(width=d.C.16.4b.4c.V$inst.max - d.C.16.4b.4c.V$inst.min) + scale_y_log10()
```

## Facet Plot

```{r Facet Plot}
facet.frame.I<-rbind(data.frame(d.B.8.4b.4c.I, class="B-8"),
                   data.frame(d.B.16.4b.4c.I, class="B-16"),
                   data.frame(d.C.8.4b.4c.I, class="C-8"),
                   data.frame(d.C.16.4b.4c.I, class="C-16"))

facet.frame.II<-rbind(data.frame(d.B.8.4b.4c.II, class="B-8"),
                   data.frame(d.B.16.4b.4c.II, class="B-16"),
                   data.frame(d.C.8.4b.4c.II, class="C-8"),
                   data.frame(d.C.16.4b.4c.II, class="C-16"))

facet.frame.III<-rbind(data.frame(d.B.8.4b.4c.III, class="B-8"),
                   data.frame(d.B.16.4b.4c.III, class="B-16"),
                   data.frame(d.C.8.4b.4c.III, class="C-8"),
                   data.frame(d.C.16.4b.4c.III, class="C-16"))

facet.frame.IV<-rbind(data.frame(d.B.8.4b.4c.IV, class="B-8"),
                   data.frame(d.B.16.4b.4c.IV, class="B-16"),
                   data.frame(d.C.8.4b.4c.IV, class="C-8"),
                   data.frame(d.C.16.4b.4c.IV, class="C-16"))

facet.frame.V<-rbind(data.frame(d.B.8.4b.4c.V, class="B-8"),
                   data.frame(d.B.16.4b.4c.V, class="B-16"),
                   data.frame(d.C.8.4b.4c.V, class="C-8"),
                   data.frame(d.C.16.4b.4c.V, class="C-16"))

ggplot(facet.frame.I, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=elements)) + geom_point() + geom_linerange() + scale_y_log10() + facet_wrap(~ class)

ggplot(facet.frame.II, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=elements)) + geom_point() + geom_linerange() + scale_y_log10() + facet_wrap(~ class)

ggplot(facet.frame.III, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=elements)) + geom_point() + geom_linerange() + scale_y_log10() + facet_wrap(~ class)

ggplot(facet.frame.IV, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=elements)) + geom_point() + geom_linerange() + scale_y_log10() + facet_wrap(~ class)

ggplot(facet.frame.V, aes(x=inst.avg, y=time.avg, ymin=time.min, ymax=time.max, color=elements)) + geom_point() + geom_linerange() + scale_y_log10() + facet_wrap(~ class)
```

